WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-14 paper/ms.tex
typo fixes

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.48\textwidth]{f2.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{
      %TODO: final number
        {\bf TESS saw WASP-4b transit earlier than expected.}
        Both plots show observed transit times minus the pre-TESS
        ephemeris as a function of transit number.  Blue curves are
        the $\pm 1\sigma$ credible interval around the constant-period
        prediction.  {\it Top:} The full timing dataset spans 10
        years.  Less precise points are more transparent.  {\it
        Bottom:} The binned TESS observation (red point) arrived $77.8
        \pm 10.8\ {\rm seconds}$ before it was expected.
        \label{fig:arrived_early}
    }
\end{figure}

@@

Having defined the free and fixed parameters, %we calculated an initial
%guess for the free parameters by maximizing the likelihood.  W
we then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
Table~1 gives the results, which are in reasonable agreement with the
parameters reported by {\it e.g.},
\citet{southworth_high-precision_2009} and 
\citet{huitson_gemini_2017}.

@@

\tablecomments{
  (A) From phase-folded TESS lightcurve (\S~\ref{sec:measurement}).
  Orbital periods are in Table~4. The limb darkening parameters were
  allowed to float around the \citet{claret_limb_2017} prediction, but
  were unconstrained.
  (B) \citep{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) From functions of stellar, transit or RV parameters as discussed in text.
  (F) {\it Gaia} DR2.
  (G) \citet{stassun_TIC_2018}.
}

>>>>

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.48\textwidth]{f2.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        {\bf TESS saw WASP-4b transit earlier than expected.} Both
        plots show observed transit times minus the pre-TESS ephemeris
        as a function of transit number.  Blue curves are the $\pm
        1\sigma$ credible interval around the constant-period
        prediction.  {\it Top:} The full timing dataset spans 10
        years.  Less precise points are more transparent.  {\it
        Bottom:} The binned TESS observation (red band) arrived $81.5
        \pm 11.8\ {\rm seconds}$ before it was expected.
        \label{fig:arrived_early}
    }
\end{figure}

@@

Having defined the free and fixed parameters, we then sampled over the
posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.  Table~1 gives the results, which
are in reasonable agreement with the parameters reported by {\it
e.g.}, \citet{southworth_high-precision_2009} and
\citet{huitson_gemini_2017}.

@@

\tablecomments{
  (A) From phase-folded TESS lightcurve (\S~\ref{sec:measurement}).
  Orbital periods are in Table~4. The limb darkening parameters were
  allowed to float around the \citet{claret_limb_2017} prediction, but
  were unconstrained.
  (B) \citet{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) From functions of stellar, transit or RV parameters as discussed in text.
  (F) {\it Gaia} DR2.
  (G) \citet{stassun_TIC_2018}.
}
